---
title: "Reproducible Pitch Presentation"
author: "Cesar Aguirre Rivadeneira"
date: "15/8/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Course Project

Your Shiny Application

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

## Application usage

Taking advance on the diamonds dataset from de ggplot package, the shiny app created is going to predict the diamond price given the carat using a slider, the color and the cut selecting the values on a selector. 

You can find the app on: 
https://cesaraguirrerivadeneira.shinyapps.io/ShinyDiamondsCesarAguirre/

You can find all the code from the app in the repository:
https://github.com/CesarAguirreRivadeneira/DevelopingDataProducts

## Diamonds dataset

```{r ddd, echo = TRUE}
library(ggplot2)
summary(diamonds)
```

## Diamonds plot overview

```{r diamonds}
plot(diamonds$carat, diamonds$price, xlab = "Diamonds Price", ylab = "Carat", bty = "n",col=as.factor(diamonds$color),ylim = c(50, 20000))
```

